Catchability_ecov_sims

### 2023-09-22 Ecov_study/catchability/Catchability_ecov_sims.Rmd
Update simulations.

Load packages & source functions used in simulation testing
```{r}
# Packages
library(tidyverse)
library(wham)
# Simulation testing functions
source(here::here("Ecov_study","catchability","simOM.R"))
source(here::here("Ecov_study","catchability","simTestWHAM.R"))
```

@@

## Post-process results

```{r}

@@

## Generic stock info that is never misspecified/changed
```{r}
# Pull generic groundfish life history/data
source(file.path(here::here(),"common_code", "make_basic_info.R"))
groundfish_info <- make_basic_info()

# Assume logistic selectivity for the fleet and all indices
sel_list <- list(model = c(rep("logistic", groundfish_info$n_fleets),rep("logistic", groundfish_info$n_indices)),
                   initial_pars = rep(list(c(5,1)), groundfish_info$n_fleets + groundfish_info$n_indices),
                 n_selblocks = c(groundfish_info$n_fleets + groundfish_info$n_indices)) #fleet, index

# Starting mean M estimate at 0.2, estimate constant M for all ages/years
M <- list(initial_means = rep(0.2, length(groundfish_info$ages)))

# Assume random about the mean recruitment, beverton-holt stock recruit didn't converge with an invertible hessian
recruit_model <- 2 
# NAA_list <- list(sigma="rec") # Recruitment random effects so stock recruit function implemented

genericInput <- prepare_wham_input(basic_info = groundfish_info, 
                                   selectivity = sel_list, 
                                   recruit_model = recruit_model) #,
                                   #NAA_re = NAA_list)
genericFit <- fit_wham(genericInput, MakeADFun.silent = TRUE, do.retro = FALSE, do.osa = FALSE)

## Define Operating Models (OMs)

All OMs should have catchability linked to an environmental covariate
but may differ in - Uncertainty around this relationship #!!!!!!!! -
Sign of this relationship (+/-) #!!!!!!!!

Set up input and fit OM1

```{r}
inputOM1 <- prepare_wham_input(model_name = "OM1") #!!!!!!!!!!!!
OM1 <- fit_wham(inputOM1, do.osa = FALSE, do.retro = FALSE, MakeADFun.silent = TRUE)
```

## Define Estimation Models (EMs)

| q-Env link                    | Seasonal misspecification |
| ----------------------------- | ------------------------- |
| Without link                  | Both seasons correct (q-Env link in EM and OM)         |
| With link                     | 1 season misspecified (q-Env linked but no link in OM) |
| Without link, q random effect | Both seasons misspecified (no link but link in OM)     |
| With link, q random effect    | |

Correctly specified link between catchability and the environment

```{r}
EMq_env <- prepare_wham_input(model_name = "EMq_env")
```

Catchability random effect and a link between catchability and the
environment

```{r}
EMq_rand_env <- prepare_wham_input(model_name = "EMq_rand_env")
```

Only a catchability random effect, fit to environmental model without
link

```{r}
EMq_rand <- prepare_wham_input(model_name ="EMq_rand")
```

No catchability considerations (i.e. status quo), fit to environmental
model without link !!!! how does this work if you feed in the ecov_beta?

```{r}
EMq <- prepare_wham_input(model_name = "EMq")
```

## Simulation testing

```{r}
simTestWHAM(nsim = 5, OM = OM1, inputEMlist = list(EMq_env, EMq_rand_env, EMq_rand, EMq)) # Update once OM/EM specifics finalized!!!!

@@

>>>>

Load packages & source functions used in simulation testing
```{r}
## Packages
library(tidyverse)
library(wham)

## OM/EM setup function
# source(here::here("Project_0", "code", "make_om.R"))
source(here::here("make_om.R")) # From Project_0/code/make_om.R
# source(file.path(here::here(),"common_code", "make_basic_info.R"))
source(here::here("make_basic_info.R"))

## Simulation testing functions
# source(here::here("Ecov_study","catchability","simOM.R"))
source(here::here("Other_Research", "simOM.R"))
# source(here::here("Ecov_study","catchability","simTestWHAM.R"))
source(here::here("Other_Research", "simTestWHAM.R"))

@@

## Set up operating and estimation models
This need only be done once by running Setup_OMs.Rmd !!! Need to move this code here so OMsetup and EMsetup available below for processing

## Simulation testing
```{r}
simTestWHAM(nsim = 5, OM = OM1, inputEMlist = list(EMq_env, EMq_rand_env, EMq_rand, EMq)) # Update once OM/EM specifics finalized!!!!

@@

Run tests only for EMs with no seasonal misspecifications (only catchability misspecification misspecified)
```{r}
subsetEM <- EMsetup %>% as.data.frame() %>% filter(miss_season == "NONE")

for(iom in 1:192){
  testOM <- readRDS(here::here("Results", paste0("OM_", iom, ".Rds")))

  for(iem in 1:4){
    testEM <- readRDS(here::here("Results", paste0("OM_", iom), paste0("EM_missSeason_", subsetEM[iem, "miss_season"], "_missQ_", subsetEM[iem, "miss_q"]), "EMinput.Rds"))
  }
}
```

Run OMs with no ecov effect (NoEcov) and with ecov effect (Ecov) are equivalent here and the qRand and qRandEcov are also equivalent so only run the NoEcov and qRandEcov options
```{r}
subsetOM <- OMsetup %>% filter(Ecov_effect == 0)
# EMs 
subsetEM <- Msetup %>% filter(miss_season == "NONE") %>% filter(miss_q == "qRand" | miss_q == "NoEcov")
```

@@

# 9/18/23
1) do OM & EM setup (EMs specified relative to each OM)
```{r}
Setup_OMs()
```
2) simulation test EMs for each OM
```{r}
simTestWHAM()
```
3) Post-process results
```{r}
postprocess_simTestWHAM()
```
